Meuse river annual maximal discharge

### 2022-03-16 Practicals/Day1_MEUSE.Rmd
Saved changes to: Code_examples/plot_wind.R Practicals/Day1_MEUSE.Rmd Practicals/Day1_MEUSE.html

```{r}
# import meuse data
source("meuse.data.R")
attach(meuse)
require(lattice)
names(meuse)
xyplot(Discharge~Year,pch=19)
```

@@

```{r}
qqmath(Discharge,xlab="Normal quantiles")
# QQplot for Extreme Value Analysis
qqmath(Discharge,distribution = qexp,xlab="Exponential quantiles")

@@

```{r}
meuse.GEV=gev.fit(Discharge)
meuse.GUM=gum.fit(Discharge)
# plot diagnostics
gev.diag(meuse.GEV)
gum.diag(meuse.GUM)
```
```{r}
gev.profxi(meuse.GEV)   #-.3,.3
gev.prof(meuse.GEV,100) # 2500,4500
```
CONCLUSION
=

@@

```{r}
# there seems to be an outlier: which year?
plot(meuse)
###  For interactivity execute the commands of chunk in the CONSOLE
# CLICK on point in Plot window [ESC  to end]
identify(meuse)
```

@@

```{r}
Year[15]; Year[85]

@@

```{r}
mm2 = data.frame(cbind(Year[c(-15,-85)],Discharge[c(-15,-85)]))
colnames(mm2) = c("Year","Discharge")
```

>>>>

```{r}
# import meuse data
source("Day1_meuse.data.R")
attach(meuse)
require(lattice)
names(meuse)
xyplot(Discharge~Year,pch=5)
```

@@

```{r}
qqmath(Discharge,xlab="Normal quantiles")
#abline(a = 1, b = 0)
# QQplot for Extreme Value Analysis
qqmath(Discharge,distribution = qexp,xlab="Exponential quantiles")

@@

```{r}
meuse.GEV=gev.fit(Discharge)
meuse.GUM=gum.fit(Discharge)
# plot diagnostics
gev.diag(meuse.GEV)
gum.diag(meuse.GUM)
```
```{r}
gev.profxi(meuse.GEV,-.3,.3)
gev.prof(meuse.GEV,100, 2500,4500)
```
CONCLUSION
=

@@

```{r}
# there seems to be an outlier: which year?
plot(meuse)
###  For interactivity execute the commands of chunk in the CONSOLE
# CLICK on point in Plot window [ESC  to end]
identify(meuse)
which.max(meuse$Discharge)
```

@@

```{r}
Year[15]; Year[83]

@@

```{r}
mm2 = data.frame(cbind(Year[c(-15,-83)],Discharge[c(-15,-83)]))
colnames(mm2) = c("Year","Discharge")
```
